Virtual Memory Assisted Transactional Memory for Dynamic Languages

### 2014-06-03 talk/dls2014/paper/paper.tex
Footnote: remap_file_pages

The next step involves using \lstinline!remap_file_pages()!, a Linux
system call, to establish the \emph{fully-shared configuration}.  All pages
of segments $>0$ map to the pages of the sharing-segment.

>>>>

The next step involves using \lstinline!remap_file_pages()!, a Linux
system call\footnote{remap\_file\_pages() can also be done with more mmap()
calls in a roughly portable way, but the former is more efficient on Linux.},
to establish the \emph{fully-shared configuration}.  All pages
of segments $>0$ map to the pages of the sharing-segment.
